---
title: "Improving Comprehension of Measurements Using Concrete Re-expression Strategies: Usefulness Study - Re-expressions versus Random Re-expressions"
author: "Jessica Hullman"
date: "12/30/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(lme4)
library(plyr)
```

## Load Data
Description: Study is between subjects repreated measures, workers completed 15 trials presentng news article where a highlighted measurement(s) was re-expressed using randomly drawn objects from the database or was re-expressed using Adding Familiar Context or Reunitization. 
Remember to navigate to the directory with this file and the data file using setwd(). Use getwd() to check your current directory

```{r}
ads <- read.csv("./chi_study2_forR_random.txt", sep="\t", header=TRUE)
nrow(ads) 
ads <- subset(ads, ads$drop!=1)
nrow(ads) 

#Number of workers
unique(ads$workerId)

```

## Set up
Transform variables, check count per condition


```{r} 
ads$rand <- as.factor(ads$rand)
ads$q2rate <- ads$q2rate + 1
ads$q1YN <- as.numeric(ads$q1YN)

summary(ads$cond)
```
#Summary stats
Response to Q1 - Is the article content helpful for understanding the highlighted measurement
Response to Q2 - Rate your level of agreement with the statement, the article content is helpful for understanding the highlighted measurement

```{r}
ddply(ads, ~cond, summarise, mean=mean(q1YN, na.rm=TRUE), sd=sd(q1YN, na.rm=TRUE))
ddply(ads, ~cond, summarise, mean=mean(q2rate, na.rm=TRUE), sd=sd(q2rate, na.rm=TRUE))
```

#Subset data for models
Proportional analogy and the No Re-expression treatments for pairs of measurements
Adding Familiar Content, Reunitization, and the No Re-expression treatments for single measurements

```{r}
ads_pa <- subset(ads, ads$cond=="pa" | ads$task == "offS::11::3_4" | ads$task=="offS::13::6_10" | ads$task=="offS::17::3_4" | ads$task=="offS::2::2_4" | ads$task=="offS::4::0_3") 
nrow(ads_pa) #151
ads_reint <- subset(ads, ads$cond != "pa")
nrow(ads_reint) #383 

ads_reint <- subset(ads_reint, ads_reint$task != "offS::11::3_4" & ads_reint$task!="offS::13::6_10" & ads_reint$task!="offS::17::3_4" & ads_reint$task!="offS::2::2_4" & ads_reint$task!="offS::4::0_3")
nrow(ads_reint) #302
```

#Remove Proportional Analogy and Off Trials - 1st study already compares


```{r}

ads <- subset(ads, ads$cond!="pa") #365
ads <- subset(ads, ads$cond!="off") #293
```

#Summary stats
Response to Q1 - Is the article content helpful for understanding the highlighted measurement
Response to Q2 - Rate your level of agreement with the statement, the article content is helpful for understanding the highlighted measurement

```{r}
ddply(ads, ~cond, summarise, mean=mean(q1YN, na.rm=TRUE), sd=sd(q1YN, na.rm=TRUE))
ddply(ads, ~cond, summarise, mean=mean(q2rate, na.rm=TRUE), sd=sd(q2rate, na.rm=TRUE))
```


#Adding Familiar Context, Reunitization, and Random  - Q1
Mixed effects logistic regression to compare probability of responding "Yes" to Q1

```{r}
mQ1 <- glmer(q1YN ~  reunit + rand + order + (1 | workerId), data = ads, family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 10)
summary(mQ1)
```


Coefficients for fixed effects, with intervals (95%, on logit scale) and odds ratios

```{r}
se <- sqrt(diag(vcov(mQ1)))
tab <- cbind(Est = fixef(mQ1), LL = fixef(mQ1) - 1.96 * se, UL = fixef(mQ1) + 1.96 * se)

print(exp(tab), digits=3)
```

Change to express how much more likely you are to say Y to Q1 in adding familiar context, with CI

```{r}
1/0.0685 
1/0.16
1/0.03
````


Mixed effects linear regression to compare helpfulness ratings for Q2


```{r}
full.model <- lmer(q2rate  ~ reunit + rand + (1 | workerId), data = ads)
summary(full.model)

#Checking model significance  - NHST
null_rand.model <- lmer(q2rate  ~ reunit + (1 | workerId), data = ads)
anova(full.model,null_rand.model)
```

Coefficients for fixed effects and and 95% confidence intervals

```{r}
fixef(full.model)
confint(full.model)
```

