---
title: 'Improving Comprehension of Measurements Using Concrete Re-expression Strategies:
  Estimation Study'
author: "Jessica Hullman"
date: "12/31/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read in data

Responses for Adding Familiar Context and Reunitization are in separate files (workers did one or the other along with No Re-expression trials in the within-subjects design)

```{r}
adsc <- read.csv("result_context.csv", sep=",", header=TRUE)
nrow(adsc) #960

adsr <- read.csv("result_reunit.csv", sep=",", header=TRUE)
nrow(adsr) # 960

```

## Summary stats


```{r}
summary(adsc)
summary(adsr)

ddply(adsc, ~cond, summarise, mean=mean(abs_diff_ratio, na.rm=TRUE), sd=sd(abs_diff_ratio, na.rm=TRUE))

ddply(adsr, ~cond, summarise, mean=mean(abs_diff_ratio, na.rm=TRUE), sd=sd(abs_diff_ratio, na.rm=TRUE))

```

#Adding Familiar Context vs No Re-expressions

```{r}
context.model <- lmer(abs_diff_ratio  ~ integ_d + order_n  + (1 | token) + (1 |task), data=adsc)
summary(context.model)

```

Coefficients and confidence intervals (95%)

```{r}
fixef(context.model)
confint(context.model)
```

NHST method - checks for reliable difference when condition is taken into account

```{r}
nullcontext.model <- lmer(abs_diff_ratio  ~  order_n + (1 | token) + (1 |task), data=adsc)
anova(context.model, nullcontext.model)
```

#Reunitization vs No Re-expressions

```{r}
reunit.model <- lmer(abs_diff_ratio  ~ reunit_d + order_n  + (1 | token) + (1 |task), data=adsr)
summary(reunit.model)

```

Coefficients and confidence intervals (95%)

```{r}
fixef(reunit.model)
confint(reunit.model)
```

NHST method - checks for reliable difference when condition is taken into account

```{r}
nullreunit.model <- lmer(abs_diff_ratio  ~  order_n +(1 | token) + (1 |task), data=adsr)
anova(reunit.model, nullreunit.model)
```

